Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-10-20 summary.Rmd
temp commit

>>>>

In these simulations, Algorithm 2 is compared against sparse subspace clustering \cite{soltanolkotabi2014} \cite{noroozi2019estimation} and modularity maximization \cite{307cbeb9b1be48299388437423d94bf1}, and Algorithm 3 is compared against an 
MLE-based estimator \cite{noroozi2019estimation} and modularity maximization 
\cite{307cbeb9b1be48299388437423d94bf1}.
